Notes and code examples to accompany "If the Null Fits, You Must Omit

### 2025-12-10 index.qmd
restructured

Change directories to go to the `gp-statmod/GroupPolarizationStatmod` directory where this document lives:

```         
cd gp-statmod/GroupPolarizationStatmod
```

@@

@@

This is used inside the `calc_fdr_vs_significance` function that adds another column to
this dataframe, the false discovery rate (FDR) for a set of significance values. Here it
is being called with the default metascience parameters with a base rate of $b=0.1$ and a
statistical power of $W=0.8$. We consider three effect sizes in this paper according to
the : "small", "medium", and "large" effect sizes traditionally assumed practically
meaningful across social sciences [@CohenBook1988]. I put this function in the `scripts` directory because to run the full analyses presented in the paper it's only necessary to run `calc_fdr_vs_significance` since it creates a column for the false positive rate and the estimated false detection rate calculated for each experimental design we studied.

@@

I again call the function with the defaults specified, for illustration. Remember the `significance_vals` map to _effect-detection thresholds_ ($d^*$) in the paper.

@@

fdr_over_thresholds <- calc_fdr_vs_significance(
  probit_fits_dir = probit_fits_dir,  # defined in above code block
  base_rate = 0.1, power = 0.8, significance_vals = c(0.2, 0.5, 0.8)
)

>>>>

Change directories to go to the `gp-statmod/docs` directory where this document lives:

```         
cd gp-statmod/docs
```

@@

This tutorial is still valuable if you're just reading it on the [code documentation associated with the journal article](https://mt-digital.github.io/gp-statmod).

@@

This is used inside the `calc_fdr_vs_significance` function that adds another column to
this dataframe, the false discovery rate (FDR) for a set of significance values. Here it
is being called with the default metascience parameters with a base rate of $b=0.1$ and a
statistical power of $W=0.8$. We consider three effect-detection thresholds in the paper: "small", "medium", and "large" effect sizes traditionally assumed practically
meaningful across social sciences [@CohenBook1988].

@@

I put this function in the `scripts` directory because to run the full analyses presented in the paper it's only necessary to run `calc_fdr_vs_significance` since it creates a column for the false positive rate and the estimated false detection rate calculated for each experimental design we studied.

Below I call the function with the defaults specified, for illustration. Remember the `significance_vals` map to _effect-detection thresholds_ ($d^*$) in the paper.

@@

# This 
fdr_over_thresholds <- calc_fdr_vs_significance(
  probit_fits_dir = probit_fits_dir,  # defined in above code block
  base_rate = 0.1, power = 0.8, significance_vals = c(0.2, 0.5, 0.8)
)
